Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-02-05 analysis/paper/paper.Rmd
re-knit paper after selecting new habitat metrics for QRF. Added some text about the extrapolation model to the discussion.

<!-- Start with benefits of extrapolation model. For example, allows us to make estimates at larger scales. However, transition to negatives of extrapolation model. -->

<!-- Then open it up to next steps of extrapolation model. i.e., ideally one should collect spatially continuous habitat data. If done, we could eliminate the extrapolation model altogether. Transition to improving habitat data. -->

While the Columbia River Basin is an excellent candidate for this type of extrapolation given the wealth of CHaMP data, application of this technique to areas with limited habitat data may be considerably more challenging. On-the-ground habitat data collection is costly, time-consuming, and often not reproducible; thereby limiting the effectiveness of this type of extrapolation.  Additionally, the extrapolation model relies on Global Available Attribute (GAA) data which ….

>>>>

Our extrapolation model was focused on extrapolating to other master sample points, because that is the dataset available to us, but the methodology could be improved. Extrapolating to reaches on a stream network, as opposed to points on the landscape, could improve the interpretability of the results. This would require a stream network with relevant attributes attached to each reach, similar to the GAAs we used. Another approach could be to move towards sampling habitat in a more spatially continuous fashion, covering most or all of a watershed, and builting a QRF model from that dataset. Even if the fish data was not done continously, estimates of capacity could be made directly from the QRF model across the entire stream network, without the need for an extrapolation model.

<!-- Do we need any more in this section? I commented out the paragraph below... -->

<!-- While the Columbia River Basin is an excellent candidate for this type of extrapolation given the wealth of CHaMP data, application of this technique to areas with limited habitat data may be considerably more challenging. On-the-ground habitat data collection is costly, time-consuming, and often not reproducible; thereby limiting the effectiveness of this type of extrapolation.  Additionally, the extrapolation model relies on Global Available Attribute (GAA) data which ….  -->
